Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-26 manuscripts/manuscript.Rmd
working through minor manuscript edits

Such patterns of variable stocks managed
under far less variable quotas are extremely common; for instance, 
in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the righthand panels [@SEDAR2013]. Though the stock assessment
shows similarly frequent variation between 1994 and 2012, the quota has
only been adjusted twice during this period. In contrast to the adjustment
in the bluefin quotas, both adjustments in snowy grouper quotas were phased
in through steps over several years: 1994-96 and 2005-08.
More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

>>>>

Such patterns of variable stocks managed
under far less variable quotas are extremely common, as in the instance of 
the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
shown in the righthand panels [@SEDAR2013]. Though the stock assessment
shows similarly frequent variation between 1994 and 2012, the quota has
only been adjusted twice during this period. In contrast to the adjustment
in the bluefin quotas, both adjustments in snowy grouper quotas were phased
in through steps over several years: 1994-96 and 2005-08.
More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.
